# Getting and cleaning data course project

```{r "Initialization"}
opts_chunk$set(cache=TRUE)
rm(list=ls())
```


```{r}
library(data.table)
```

### Download data
```{r}
zipFileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
zipFileName <- "data//uci-har-dataset.zip"

if(!file.exists(zipFileName)){
    download.file(zipFileUrl, zipFileName, method="curl")
}
```
```{r "Read Data"}
#list files in zipFile
unzip(zipFileName, list=TRUE)$Name

activityLabelFileName <- 'UCI HAR Dataset/activity_labels.txt'
featureFileName <- 'UCI HAR Dataset/features.txt'
trainFileName <- "UCI HAR Dataset/train/X_train.txt"
trainSubjectFileName <- "UCI HAR Dataset/train/subject_train.txt"
trainActivityFileName <- "UCI HAR Dataset/train/y_train.txt"
testFileName <- "UCI HAR Dataset/test/X_test.txt"
testSubjectFileName <- "UCI HAR Dataset/test/subject_test.txt"
testActivityFileName <- "UCI HAR Dataset/test/y_test.txt"

activityLabel <- read.table(unz(zipFileName, activityLabelFileName))
feature <- read.table(unz(zipFileName, featureFileName))
train <- read.table(unz(zipFileName, trainFileName))
trainSubject <- read.table(unz(zipFileName, trainSubjectFileName))
trainActivity <- read.table(unz(zipFileName, trainActivityFileName))
test <- read.table(unz(zipFileName, testFileName))
testSubject <- read.table(unz(zipFileName, testSubjectFileName))
testActivity <- read.table(unz(zipFileName, testActivityFileName))

```

```{r}

```



# files required for analysis one for train and one for test
# activity_labels.txt - map activities to code
# (test|train)/subject_train.txt contains the subject id for each observation
# (test|train)/X_train.txt for the accelerometer vectors
# (test|train)/y_train.txt activity code for each observations
# (test|train)/
# (test|train)
# (test|train)
# (test|train)